### 2025-01-17 README.Rmd
fixes to list on CRAN

```{r}
library(qmj)
companies <- qmjdata::companies ## Stores company names and tickers from the Russell 3000 index.
financials <- qmjdata::financials ## Stores financial documents for the given list of companies.
prices <- qmjdata::prices ## Stores price returns and closing stock prices for the past two years.
quality <- qmjdata::quality ## Stores the quality scores and the scores of its components.
```

@@

```{r}
market_data(companies, financials, prices)
```

@@

```{r}
market_profitability(companies, financials)
```

>>>>

```{r}
library(qmj)
companies_r3k16   ## Stores company names and tickers from the Russell 3000 index.
financials_r3k16  ## Stores financial documents for the given list of companies.
prices_r3k16      ## Stores price returns and closing stock prices for the past two years.
quality_r3k16     ## Stores the quality scores and the scores of its components.
```

@@

```{r}
market_data(companies_r3k16, financials_r3k16, prices_r3k16)
```

@@

```{r}
market_profitability(companies_r3k16, financials_r3k16)
```
